### 2021-12-06 README.Rmd
add badges

>>>>

[![CRAN status](https://www.r-pkg.org/badges/version/skater)](https://CRAN.R-project.org/package=skater)

[![biorXiv](https://img.shields.io/badge/biorXiv-10.1101%2F2021.07.21.453083-red)](https://www.biorxiv.org/content/10.1101/2021.07.21.453083v1)

[![DOI](https://zenodo.org/badge/339462170.svg)](https://zenodo.org/badge/latestdoi/339462170)
